Disentangling patterns of gene expression in high grade serous ovarian cancer by matrix factorization

### 2020-08-09 MSc_Dissertation_B156476.tex
Treatment options; improved HGSOC expression section; removed copied figure
Figure[ht], WGD boxplots, grid of scatter plots * Added [ht] to all begin{figure} * Incorporated boxplot for WGD (may remove) and grid of scatter plots,   with caption.

\subsection{Epithelial Ovarian Cancer}
\label{{sec-epithelial-ovarian-cancer}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.4]{Sompairac_ICA_NMF_PCA.png}
\end{center}
\caption{Illustrating the differing results of component extraction by PCA, ICA and NMF.  From \cite{Sompairac2019}}
\label{fig-pca-ica-nmp-explanation}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.7]{methodlology_overview.pdf}
\end{center}
\caption{Overview of methodology as information flow.  The diagramatic convention here is that at each stage, both datasets -- TCGA and AOCS -- are processed separately by the given algorithm.  The exception is Gene Set Intersection, which involves interaction between the datasets.}
\label{fig-method-overview}
\end{figure}
In outline our method is follows:
\begin{enumerate}
\item
Identification of a consistent gene set between the TCGA and AOCS datasets.
\item
Unsupervised metagene extraction by matrix factorization methods : NMF, ICA and PCA.
\item
Metagene selection for robustness by k-means clustering of bootstrap resampled factorizations evaluated by silhouette score, based on the TCGA dataset.
\item
Investigation of biological significance of determined factors by gene enrichment analysis against the Gene Ontology (GO).
\item
Computation by least squares optimisation of metasamples associated with with each TCGA derived metagene against TCGA and AOCS datasets.
\item
Alignment of available metadata with computed metasamples, for TCGA and AOCS.
\item 
Survival analysis on TCGA and AOCS to investigate relationship between metasamples and patient survival.
\item
Clustered heatmaps to visualise relationships between metasamples, patients and metadata.
\end{enumerate}

@@

\begin{figure}
\begin{center}
\begin{Verbatim}[baselinestretch=1, frame=single, rulecolor=\color{blue}, label=Metagene Stability Assessment, fontfamily=courier, fontsize=\small]

@@

%%%%%%%%%%% RESULTS %%%%%%%%%%%%%
% \afterpage{\clearpage}

@@

\def\S{0.4}
\begin{figure}
\begin{center}
\includegraphics[scale=\S]{\plotspath{AOCS_Protein/FactorClustering/multiple_single_factors_scatter_AOCS_ICA_2_3_5_10_fixed.pdf}} \\
\includegraphics[scale=\S]{\plotspath{AOCS_Protein/FactorClustering/multiple_single_factors_scatter_AOCS_ICA_2_3_5_10_bootstrap.pdf}}\\
\caption{Clustering of metagenes from ICA facorizations on the N=80 AOCS dataset, comparing \emph{fixed} sampling (top row) with \emph{bootstrap} sampling (bottom row) for a selection of factorization ranks.  }
\label{fig-AOCS-ica-fixed-vs-bootstrap}
\label{fig-first-cluster-result}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[scale=\S]{\plotspath{TCGA_OV_VST/FactorClustering/multiple_single_factors_scatter_TCGA_ICA_2_3_5_10_fixed.pdf}} 
\includegraphics[scale=\S]{\plotspath{TCGA_OV_VST/FactorClustering/multiple_single_factors_scatter_TCGA_ICA_2_3_5_10_bootstrap.pdf}}
\caption{Clustering of metagenes from ICA facorizations on the N=374 TCGA dataset, again comparing fixed and bootstrap sampling.}
\label{fig-TCGA-ica-fixed-vs-bootstrap}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=\S]{\plotspath{TCGA_OV_VST/FactorClustering/multiple_single_factors_scatter_TCGA_NMF_2_3_5_10_bootstrap.pdf}} \\
\includegraphics[scale=\S]{\plotspath{TCGA_OV_VST/FactorClustering/multiple_single_factors_scatter_TCGA_ICA_2_3_5_10_bootstrap.pdf}} \\
\includegraphics[scale=\S]{\plotspath{TCGA_OV_VST/FactorClustering/multiple_single_factors_scatter_TCGA_PCA_2_3_5_10_bootstrap.pdf}} \\
\includegraphics[scale=0.55]{\plotspath{/TCGA_OV_VST/FactorClustering/silhouette_plots_TCGA_2_3_4_5_6_7_8_9_10_bootstrap.pdf}} 
\caption{Metagene clustering for all three methods applied to the N=374 TCGA dataset with bootstrap sampling, over a range of factorization ranks.  The silhouette scores are also plotted (bottom).  It is on the basis of this figure that the factorization ranks for each method were selected.}
\label{fig-TCGA-all-bootstrap}
\label{fig-last-cluster-result}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{\plotspath{TCGA_OV_VST/GeneEnrichment/component_jaccard_heatmap.pdf}}
\end{center}
\caption{Heatmap of Jaccard similarities between the candidate genes identified by the 11 components.}
\label{fig-component-jaccard-similarities}
\end{figure}

@@

\begin{figure}[hb]
\begin{center}
\includegraphics[scale=0.14]{\plotspath{TCGA_OV_VST/GeneEnrichment/go_lineage_1_of_NMF_3.png}} \\
\begin{spacing}{0.6}
{\small Genes: \tiny \input{/home/ipoole/Documents/gitrepos/HgsocTromics/Plots/TCGA_OV_VST/GeneEnrichment/go_gene_set_1_of_NMF_3.txt}}
\end{spacing}
\vspace{0.5cm}
{\small Component NMF-1-of-3} \\
\vspace{1cm}
\includegraphics[scale=0.14]{\plotspath{TCGA_OV_VST/GeneEnrichment/go_lineage_2_of_NMF_3.png}} \\
\begin{spacing}{0.6}
{\small Genes: \tiny \input{/home/ipoole/Documents/gitrepos/HgsocTromics/Plots/TCGA_OV_VST/GeneEnrichment/go_gene_set_2_of_NMF_3.txt}}
\end{spacing}
\vspace{0.5cm}
{\small Component NMF 2-of-3} \\
\caption{Lineage maps of enriched Gene Ongology (GO) terms for components NMF-1-of-3 and NMF-2-of-3.  In these diagrams, enriched terms are coloured purple, while there ancestors in the ontology are yellow.  (NMF-3-of-3 produced no significant enrichment results)}
\label{fig-NMF-go-lineage}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[scale=0.1]{\plotspath{TCGA_OV_VST/GeneEnrichment/go_lineage_3_of_ICA_5.png}} \\
\begin{spacing}{0.6}
{\small Genes: \tiny \input{/home/ipoole/Documents/gitrepos/HgsocTromics/Plots/TCGA_OV_VST/GeneEnrichment/go_gene_set_3_of_ICA_5.txt}}
\end{spacing}
\vspace{0.5cm}
{\small Component ICA-3-of-5} \\
\vspace{1cm}
\includegraphics[scale=0.07]{\plotspath{TCGA_OV_VST/GeneEnrichment/go_lineage_5_of_ICA_5.png}} \\
\begin{spacing}{0.6}
{\small Genes: \tiny \input{/home/ipoole/Documents/gitrepos/HgsocTromics/Plots/TCGA_OV_VST/GeneEnrichment/go_gene_set_5_of_ICA_5.txt}}
\end{spacing}
\vspace{0.5cm}
{\small Component ICA-5-of-5} \\
\caption{Lineage maps of enriched Gene Ongology (GO) terms for components ICA-3-of-5 and ICA-5-of-5}
\label{fig-ICA-3-5-go-lineage}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.5 \textwidth]{\plotspath{TCGA_OV_VST/GeneEnrichment/go_lineage_1_of_PCA_3.png}} \\
\begin{spacing}{0.6}
{\small Genes: \tiny \input{/home/ipoole/Documents/gitrepos/HgsocTromics/Plots/TCGA_OV_VST/GeneEnrichment/go_gene_set_1_of_PCA_3.txt}}
\end{spacing}
\vspace{0.5cm}
{\small Component PCA-1-of-3} \\
\vspace{1cm}
\includegraphics[width= \textwidth]{\plotspath{TCGA_OV_VST/GeneEnrichment/go_lineage_3_of_PCA_3.png}} \\
\begin{spacing}{0.6}
{\small Genes: \tiny \input{/home/ipoole/Documents/gitrepos/HgsocTromics/Plots/TCGA_OV_VST/GeneEnrichment/go_gene_set_3_of_PCA_3.txt}}
\end{spacing}
\vspace{0.5cm}
{\small Component PCA-3-of-3} \\
\caption{Lineage maps of enriched Gene Ongology (GO) terms for components 1 and 3 from the rank=5 PCA factorization. (Component PCA-2-of-3 produced no significant enrichment results)  }
\label{fig-PCA-1-3-go-lineage}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{\plotspath{SurvivalAnalysis/multiple_kaplan_meier_os_TCGA_TCGA.pdf}} 
\caption{Kaplan-Meier plots for each metasample component, stratified at the median value, for TCGA $\rightarrow$ TCGA for overall survival (OS) case.  Hazard ratio and p-value is shown for each case.  The final plot (bottom right) is unstratified overall survival}
\label{fig-kaplan-meier-os-TCGA-TCGA}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{\plotspath{SurvivalAnalysis/multiple_kaplan_meier_os_TCGA_AOCS.pdf}} 
\caption{Kaplan-Meier plots for TCGA $\rightarrow$ TCGA for overall survival (OS).}
\label{fig-kaplan-meier-os-TCGA-OACS}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{\plotspath{SurvivalAnalysis/multiple_kaplan_meier_pfs_TCGA_AOCS.pdf}} 
\caption{Kaplan-Meier plots for TCGA $\rightarrow$ TCGA for progression free survival (PFS).  }
\label{fig-kaplan-meier-pfs-TCGA-OACS}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{\plotspath{/SurvivalAnalysis/survival_summary_barplots_NMF.pdf}} \\
\includegraphics[scale=0.5]{\plotspath{/SurvivalAnalysis/survival_summary_barplots_ICA.pdf}} \\
\includegraphics[scale=0.5]{\plotspath{/SurvivalAnalysis/survival_summary_barplots_PCA.pdf}}
\caption{Visual summary of survival analysis as applied to TCGA(OS), AOCS(OS) and AOCS(PFS).  Plots are divided by factorization method.  Bar heights show $\log_2(\mbox{HR})$ with p-value also shown.  For a component to have robust correlation with survival we expect all three of the analysis bars to pass a significance threshold {\em and} for the $\log{\mbox{HR}}$ to to be {\em in the same sense\/}.  None achieve this.}
\label{fig-summary-survival-plots}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.7]{\plotspath{HeatMaps/clustered_heatmap_TCGA_AOCS.pdf}} 
\caption{Heatmap of the metasamples matrix for the AOCS dataset, computed from metagenes factorized from the TCGA dataset.   Several patient patient metadata variables are shown in columns to the left.  (ToDo: key for metadata colouring).}
\label{fig-heatmap-TCGA-OACS}
\end{center}
\end{figure}

@@

\section{Discussion}

>>>>

\subsection{Epithelial Ovarian Cancer}
\label{sec-epithelial-ovarian-cancer}

@@

\begin{figure}[ht]
\begin{center}
\includegraphics[scale=0.4]{Sompairac_ICA_NMF_PCA.png}
\end{center}
\caption{Illustrating the differing results of component extraction by PCA, ICA and NMF.  From \cite{Sompairac2019}}
\label{fig-pca-ica-nmp-explanation}
\end{figure}

@@

\begin{figure}[ht]
\begin{center}
\includegraphics[scale=0.7]{methodlology_overview.pdf}
\end{center}
\caption{Overview of methodology as information flow.  The diagramatic convention here is that at each stage, both datasets -- TCGA and AOCS -- are processed separately by the given algorithm.  The exception is Gene Set Intersection, which involves interaction between the datasets.}
\label{fig-method-overview}
\end{figure}
In outline our method is follows:
\begin{enumerate}
\item
Identification of a consistent gene set between the TCGA and AOCS datasets.
\item
Unsupervised metagene extraction by matrix factorization methods : NMF, ICA and PCA.
\item
Metagene selection for robustness by k-means clustering of bootstrap resampled factorizations evaluated by silhouette score, based on the TCGA dataset.
\item
Investigation of biological significance of determined factors by gene enrichment analysis against the Gene Ontology (GO).
\item
Computation by least squares optimisation of metasamples associated with with each TCGA derived metagene against TCGA and AOCS datasets.
\item
Alignment of available metadata with computed metasamples, for TCGA and AOCS.
\item 
Survival analysis on TCGA and AOCS to investigate relationship between metasamples and patient survival.
\item
Clustered heatmaps to visualise relationships between metasamples, patients and metadata.
\end{enumerate}

@@

\begin{figure}[ht]
\begin{center}
\begin{Verbatim}[baselinestretch=1, frame=single, rulecolor=\color{blue}, label=Metagene Stability Assessment, fontfamily=courier, fontsize=\small]

@@

%%%%%%%%%%% RESULTS %%%%%%%%%%%%%
\afterpage{\clearpage}

@@

\def\S{0.4}
\begin{figure}[ht]
\begin{center}
\includegraphics[scale=\S]{\plotspath{AOCS_Protein/FactorClustering/multiple_single_factors_scatter_AOCS_ICA_2_3_5_10_fixed.pdf}} \\
\includegraphics[scale=\S]{\plotspath{AOCS_Protein/FactorClustering/multiple_single_factors_scatter_AOCS_ICA_2_3_5_10_bootstrap.pdf}}\\
\caption{Clustering of metagenes from ICA facorizations on the N=80 AOCS dataset, comparing \emph{fixed} sampling (top row) with \emph{bootstrap} sampling (bottom row) for a selection of factorization ranks.  }
\label{fig-AOCS-ica-fixed-vs-bootstrap}
\label{fig-first-cluster-result}
\end{center}
\end{figure}

\begin{figure}[ht]
\begin{center}
\includegraphics[scale=\S]{\plotspath{TCGA_OV_VST/FactorClustering/multiple_single_factors_scatter_TCGA_ICA_2_3_5_10_fixed.pdf}} 
\includegraphics[scale=\S]{\plotspath{TCGA_OV_VST/FactorClustering/multiple_single_factors_scatter_TCGA_ICA_2_3_5_10_bootstrap.pdf}}
\caption{Clustering of metagenes from ICA facorizations on the N=374 TCGA dataset, again comparing fixed and bootstrap sampling.}
\label{fig-TCGA-ica-fixed-vs-bootstrap}
\end{center}
\end{figure}

@@

\begin{figure}[ht]
\begin{center}
\includegraphics[scale=\S]{\plotspath{TCGA_OV_VST/FactorClustering/multiple_single_factors_scatter_TCGA_NMF_2_3_5_10_bootstrap.pdf}} \\
\includegraphics[scale=\S]{\plotspath{TCGA_OV_VST/FactorClustering/multiple_single_factors_scatter_TCGA_ICA_2_3_5_10_bootstrap.pdf}} \\
\includegraphics[scale=\S]{\plotspath{TCGA_OV_VST/FactorClustering/multiple_single_factors_scatter_TCGA_PCA_2_3_5_10_bootstrap.pdf}} \\
\includegraphics[scale=0.55]{\plotspath{/TCGA_OV_VST/FactorClustering/silhouette_plots_TCGA_2_3_4_5_6_7_8_9_10_bootstrap.pdf}} 
\caption{Metagene clustering for all three methods applied to the N=374 TCGA dataset with bootstrap sampling, over a range of factorization ranks.  The silhouette scores are also plotted (bottom).  It is on the basis of this figure that the factorization ranks for each method were selected.}
\label{fig-TCGA-all-bootstrap}
\label{fig-last-cluster-result}
\end{center}
\end{figure}

@@

\begin{figure}[ht]
\begin{center}
\includegraphics[scale=0.5]{\plotspath{TCGA_OV_VST/GeneEnrichment/component_jaccard_heatmap.pdf}}
\end{center}
\caption{Heatmap of Jaccard similarities between the candidate genes identified by the 11 components.}
\label{fig-component-jaccard-similarities}
\end{figure}

@@

\begin{figure}[ht]
\begin{center}
\includegraphics[scale=0.14]{\plotspath{TCGA_OV_VST/GeneEnrichment/go_lineage_1_of_NMF_3.png}} \\
\begin{spacing}{0.6}
{\small Genes: \tiny \input{/home/ipoole/Documents/gitrepos/HgsocTromics/Plots/TCGA_OV_VST/GeneEnrichment/go_gene_set_1_of_NMF_3.txt}}
\end{spacing}
\vspace{0.5cm}
{\small Component NMF-1-of-3} \\
\vspace{1cm}
\includegraphics[scale=0.14]{\plotspath{TCGA_OV_VST/GeneEnrichment/go_lineage_2_of_NMF_3.png}} \\
\begin{spacing}{0.6}
{\small Genes: \tiny \input{/home/ipoole/Documents/gitrepos/HgsocTromics/Plots/TCGA_OV_VST/GeneEnrichment/go_gene_set_2_of_NMF_3.txt}}
\end{spacing}
\vspace{0.5cm}
{\small Component NMF 2-of-3} \\
\caption{Lineage maps of enriched Gene Ongology (GO) terms for components NMF-1-of-3 and NMF-2-of-3.  In these diagrams, enriched terms are coloured purple, while there ancestors in the ontology are yellow.  (NMF-3-of-3 produced no significant enrichment results)}
\label{fig-NMF-go-lineage}
\end{center}
\end{figure}

\begin{figure}[ht]
\begin{center}
\includegraphics[scale=0.1]{\plotspath{TCGA_OV_VST/GeneEnrichment/go_lineage_3_of_ICA_5.png}} \\
\begin{spacing}{0.6}
{\small Genes: \tiny \input{/home/ipoole/Documents/gitrepos/HgsocTromics/Plots/TCGA_OV_VST/GeneEnrichment/go_gene_set_3_of_ICA_5.txt}}
\end{spacing}
\vspace{0.5cm}
{\small Component ICA-3-of-5} \\
\vspace{1cm}
\includegraphics[scale=0.07]{\plotspath{TCGA_OV_VST/GeneEnrichment/go_lineage_5_of_ICA_5.png}} \\
\begin{spacing}{0.6}
{\small Genes: \tiny \input{/home/ipoole/Documents/gitrepos/HgsocTromics/Plots/TCGA_OV_VST/GeneEnrichment/go_gene_set_5_of_ICA_5.txt}}
\end{spacing}
\vspace{0.5cm}
{\small Component ICA-5-of-5} \\
\caption{Lineage maps of enriched Gene Ongology (GO) terms for components ICA-3-of-5 and ICA-5-of-5}
\label{fig-ICA-3-5-go-lineage}
\end{center}
\end{figure}

@@

\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.5 \textwidth]{\plotspath{TCGA_OV_VST/GeneEnrichment/go_lineage_1_of_PCA_3.png}} \\
\begin{spacing}{0.6}
{\small Genes: \tiny \input{/home/ipoole/Documents/gitrepos/HgsocTromics/Plots/TCGA_OV_VST/GeneEnrichment/go_gene_set_1_of_PCA_3.txt}}
\end{spacing}
\vspace{0.5cm}
{\small Component PCA-1-of-3} \\
\vspace{1cm}
\includegraphics[width= \textwidth]{\plotspath{TCGA_OV_VST/GeneEnrichment/go_lineage_3_of_PCA_3.png}} \\
\begin{spacing}{0.6}
{\small Genes: \tiny \input{/home/ipoole/Documents/gitrepos/HgsocTromics/Plots/TCGA_OV_VST/GeneEnrichment/go_gene_set_3_of_PCA_3.txt}}
\end{spacing}
\vspace{0.5cm}
{\small Component PCA-3-of-3} \\
\caption{Lineage maps of enriched Gene Ongology (GO) terms for components 1 and 3 from the rank=5 PCA factorization. (Component PCA-2-of-3 produced no significant enrichment results)  }
\label{fig-PCA-1-3-go-lineage}
\end{center}
\end{figure}

@@

\begin{figure}[ht]
\begin{center}
\includegraphics[scale=0.5]{\plotspath{SurvivalAnalysis/multiple_kaplan_meier_os_TCGA_TCGA.pdf}} 
\caption{Kaplan-Meier plots for each metasample component, stratified at the median value, for TCGA $\rightarrow$ TCGA for overall survival (OS) case.  Hazard ratio and p-value is shown for each case.  The final plot (bottom right) is unstratified overall survival}
\label{fig-kaplan-meier-os-TCGA-TCGA}
\end{center}
\end{figure}

\begin{figure}[ht]
\begin{center}
\includegraphics[scale=0.5]{\plotspath{SurvivalAnalysis/multiple_kaplan_meier_os_TCGA_AOCS.pdf}} 
\caption{Kaplan-Meier plots for TCGA $\rightarrow$ TCGA for overall survival (OS).}
\label{fig-kaplan-meier-os-TCGA-OACS}
\end{center}
\end{figure}

\begin{figure}[ht]
\begin{center}
\includegraphics[scale=0.5]{\plotspath{SurvivalAnalysis/multiple_kaplan_meier_pfs_TCGA_AOCS.pdf}} 
\caption{Kaplan-Meier plots for TCGA $\rightarrow$ TCGA for progression free survival (PFS).  }
\label{fig-kaplan-meier-pfs-TCGA-OACS}
\end{center}
\end{figure}

\begin{figure}[ht]
\begin{center}
\includegraphics[scale=0.5]{\plotspath{/SurvivalAnalysis/survival_summary_barplots_NMF.pdf}} \\
\includegraphics[scale=0.5]{\plotspath{/SurvivalAnalysis/survival_summary_barplots_ICA.pdf}} \\
\includegraphics[scale=0.5]{\plotspath{/SurvivalAnalysis/survival_summary_barplots_PCA.pdf}}
\caption{Visual summary of survival analysis as applied to TCGA(OS), AOCS(OS) and AOCS(PFS).  Plots are divided by factorization method.  Bar heights show $\log_2(\mbox{HR})$ with p-value also shown.  For a component to have robust correlation with survival we expect all three of the analysis bars to pass a significance threshold {\em and} for the $\log{\mbox{HR}}$ to to be {\em in the same sense\/}.  None achieve this.}
\label{fig-summary-survival-plots}
\end{center}
\end{figure}

@@

\begin{figure}[ht]
\begin{center}
\includegraphics[scale=0.7]{\plotspath{HeatMaps/clustered_heatmap_TCGA_AOCS.pdf}} 
\caption{Heatmap of the metasamples matrix for the AOCS dataset, computed from metagenes factorized from the TCGA dataset.   Several patient metadata variables are shown in columns to the left.  (ToDo: key for metadata colouring).}
\label{fig-heatmap-TCGA-OACS}
\end{center}
\end{figure}

@@

\subsection{Metasample correlation with genomic features}

\begin{figure}[ht]
\begin{center}
\includegraphics[scale=0.6, draft=false]{\plotspath{BoxAndScatters/wgd_boxplot_NMF_TCGA_AOCS.pdf}}
\includegraphics[scale=0.6, draft=false]{\plotspath{BoxAndScatters/wgd_boxplot_ICA_TCGA_AOCS.pdf}}
\includegraphics[scale=0.6, draft=false]{\plotspath{BoxAndScatters/wgd_boxplot_PCA_TCGA_AOCS.pdf}}
\caption{Boxplots showing relationship between metasamples (derived from TCGA metagenes, applied to AOCS data) and whole genome doubling (WGD) status.  Metasamples from NMF, ICA and PCA are shown separately.  To allow convenient visualisation, each metasample is normalised to zero mean unit variance, hence between metasample variation is removed.}
\end{center}
\label{fig-wgd-boxplots}
\end{figure}

\begin{figure}[ht]
\begin{center}
\includegraphics[scale=0.54, draft=false]{\plotspath{BoxAndScatters/genomic_feature_scatters_TCGA_AOCS.pdf}} 
\caption{Grid of scatter plots to visualise the correlation between metasamples and genomic features.  In the case of WGD which has binary values (0, 1), jitter is applied for visual effect only.   Above each plot is shown a correlation coefficient $r$ and associated p-value, highlighted with '***' where $p < 0.01$.  In the case of WGD , the Point-Biserial correlation is used; for all others Pearson's r is used.}
\label{fig-genomic-scatters}
\end{center}
\end{figure}

\clearpage
\section{Discussion}
